\documentclass[a4paper,12pt]{article}

%================ PACKAGES =================%
\usepackage[left=0.42in,right=0.42in,top=0.35in,bottom=0.35in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}
\usepackage{fontawesome5}
\usepackage{tabularx}
\usepackage{setspace}
\usepackage[none]{hyphenat}
\usepackage{newtxtext}
\usepackage{newtxmath}

%================ PAGE SETTINGS =================%
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setstretch{1.05}
\sloppy

%================ SECTION STYLE =================%
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{7pt}{5pt}

%================ LIST SETTINGS =================%
\setlist[itemize]{leftmargin=*, itemsep=2pt, topsep=2pt, parsep=0pt}

\begin{document}

%================ HEADER =================%
\begin{center}
    {\fontsize{24}{26}\selectfont \textbf{M Eswar Manoj}} \\[6pt]
    
    {\large Bharinikam, Andhra Pradesh} \\[8pt]

    {\large
    \faEnvelope\ \href{mailto:eswarmanojmandavilli@gmail.com}{eswarmanojmandavilli@gmail.com}
    \hspace{0.6cm} | \hspace{0.6cm}
    \faPhone\ +91 9381909581
    } \\[5pt]

    {\large
    \faGithub\ \href{https://github.com/eswar-20}{GitHub}
    \hspace{0.8cm} | \hspace{0.8cm}
    \faLinkedin\ \href{https://www.linkedin.com/in/eswar-manoj-mandavilli-2a8456350}{LinkedIn}
    }
\end{center}

\vspace{-8pt}

%================ CAREER OBJECTIVE =================%
\section*{CAREER OBJECTIVE}
Computer Science student with strong foundations in data structures, algorithms, and software development. Passionate about building scalable applications and leveraging modern web technologies to solve real-world problems.

%================ EDUCATION =================%
\section*{EDUCATION}

\begin{tabularx}{\textwidth}{Xr}
\textbf{KL University, Vijayawada} & 2023 -- 2027 \\
Bachelor of Technology in Computer Science and Engineering & \\
CGPA: 8.6/10 & \\[5pt]

\textbf{Sri Viswa Junior College} & 2021 -- 2023 \\
Board of Intermediate Education, Andhra Pradesh & \\
CGPA: 8.8/10 & \\[5pt]

\textbf{Bhashyam School} & 2020 -- 2021 \\
Board of Secondary Education, Andhra Pradesh & \\
CGPA: 10.0/10 & \\
\end{tabularx}

%================ PROJECTS =================%
\section*{PROJECTS}

\textbf{Blood Bank Management System}

\begin{itemize}
    \item Developed a Blood Bank Management System using Spring Boot, React.js, MySQL, and REST APIs.
    \item Implemented donor registration, blood inventory tracking, authentication, and request handling.
    \item Designed a responsive user interface for seamless accessibility across devices.
    \item Optimized backend performance by improving database queries and API response times.
\end{itemize}

%================ INTERNSHIP EXPERIENCE =================%
\section*{INTERNSHIP EXPERIENCE}

\begin{tabularx}{\textwidth}{Xr}
\textbf{AI and ML Virtual Internship, AICTE EduSkills} & Oct -- Dec 2025 \\
\end{tabularx}

\begin{itemize}
    \item Learned machine learning workflows including preprocessing, training, and model evaluation.
    \item Built predictive models and explored real-world AI applications.
    \item Gained practical understanding of optimization techniques and ethical AI principles.
\end{itemize}

\vspace{4pt}

\begin{tabularx}{\textwidth}{Xr}
\textbf{Cyber Security Virtual Internship, ShadowFox} & Sept 2025 \\
\end{tabularx}

\begin{itemize}
    \item Conducted vulnerability assessments and threat analysis in simulated environments.
    \item Identified security weaknesses and applied mitigation strategies.
    \item Completed hands-on labs related to network security and risk management.
\end{itemize}

%================ TECHNICAL SKILLS =================%
\section*{TECHNICAL SKILLS}

\begin{itemize}
    \item \textbf{Programming:} Python, C, C++
    \item \textbf{Web Technologies:} HTML, CSS, React
\end{itemize}

%================ CERTIFICATIONS =================%
\section*{CERTIFICATIONS}

\begin{tabularx}{\textwidth}{Xr}
\textbf{Automation Anywhere} & Dec 2025 \\
\textbf{Multicloud Network Associate} & Aug 2025 \\
\end{tabularx}

\end{document}